Catchy Part: Surveying Users' Perceptions of Threats for Wearable Devices

### 2015-01-03 wearables_survey.tex
Fixed URL wrapping in bibliography, edited Abstract.

\usepackage{url}

@@

%\usepackage{breakurl}
%\usepackage[breaklinks]{hyperref}

@@

\begin{abstract}
There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint. These works generally focus on X and Y. However, works like these are not grounded in user research to make claims to the most relevant concerns for the average user. We surveyed 2,250 users about 74 data types, 4 recipients, and 2 devices to show users' perceptions of a wide range of wearables threats in a wide range of scenarios, along with an evaluation of which factors contribute to the severity of a threat. We also asked participants to rate 20 new technologies, as well as asked for what they think is the most likely risk associated with wearables. Our ranking for concerns can be used to guide future research in wearables security, especially research regarding protecting sensitive data and effective notifications and indicators. 
\end{abstract}

@@

\section{Introduction}
Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing to healthier living through fitness tracking. Wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing and big data, constantly capturing data and interpreting information to deliver insights to the user. Wearbles are gaining lots of attention. Forbes has named 2014 the ``Year of Wearable Technology \cite{Forbes},'' and market research companies estimate that 52\% are aware of wearables and among those, 33\% said they were likely to buy one \cite{NPD}.

>>>>

\usepackage{color}

@@

\usepackage[hyphens]{url}

@@

\begin{abstract}
We performed an online survey to examine computer users' risk perceptions surrounding current and future wearable computing devices. We controlled for the different data types that might be captured, who might have access to that data, as well as whether it was captured on a wearable device or a smartphone (i.e., an existing device with which participants were already familiar). In the end, we surveyed 2,250 users about 74 data types, 4 data recipients, and 2 devices to show users' perceptions of a wide range of wearables threats in a wide range of scenarios, along with an evaluation of which factors contribute to the severity of these threats. Following previous work, we also asked participants to perform a risk/benefit analysis comparing 20 new technologies with other well-established technologies. The results of this study can be used to guide future research in wearable device security, especially research that helps to protect sensitive data and guides the design of effective privacy notifications and indicators.
\end{abstract}

@@

\section{Introduction}
Wearable technology has many potential benefits, ranging from a more natural, human-centered interface for computing, to healthier living through fitness tracking. Wearable devices, or ``wearables,'' are the new frontier of ubiquitous computing and big data, constantly capturing data and interpreting information to deliver insights to the user. Wearbles are gaining lots of attention. Forbes has named 2014 the ``Year of Wearable Technology \cite{Forbes},'' and market research companies estimate that 52\% are aware of wearables and among those, 33\% said they were likely to buy one \cite{NPD}.
